\chapter*{\uppercase{ABSTRACT}}
\addcontentsline{toc}{section}{\bfseries \uppercase{Abstract (Tamil)}}
According to various industry reports, the rapid pace of technological advancement has led to a growing demand for up-to-date skills and knowledge in the job market. However, many individuals face challenges in identifying relevant courses and acquiring the necessary skills to meet these demands. To address this issue, a recommendation system leveraging item-based recommendation techniques, particularly cosine similarity measures, is proposed.

The system aims to assist individuals in selecting courses and developing job-relevant skillsets by analyzing a vast dataset of courses and job requirements. By employing similarity measures, the system identifies similarities between courses and job skillsets based on their content and attributes. This allows for the recommendation of relevant courses and skillsets that closely match a user's interests and career goals.

Moreover, the recommendation system is integrated into a chatbot application, providing users with a conversational interface to interact with the system. Users can engage with the chatbot to receive personalized course recommendations, inquire about specific skills, and explore career development opportunities in a conversational manner.

The performance of the chatbot-based recommendation system is evaluated using standard metrics such as precision, recall, and F1 score, ensuring reliable and personalized recommendations for users. Ultimately, the system aims to empower individuals in their career development journey, facilitating access to relevant learning resources and maximizing their potential for professional growth and success.