% Chapter 5

\chapter{\uppercase{Results and Performance Analysis}} % Main chapter title
\label{chap5}
The complexity analysis provides insights into the efficiency of the algorithms used in our recommendation system in terms of time and space requirements.

\section{Time Complexity}

The time complexity of the recommendation algorithms utilized in our project can be approximated as $O(n \log n)$, where $n$ is the number of available items (courses or job skillsets). The primary factor contributing to this complexity is the sorting operation performed on the available items to determine the most relevant recommendations. The sorting operation typically has an average time complexity of $O(n \log n)$ when using efficient sorting algorithms. Thus, as the number of available items increases, the time required to generate recommendations scales logarithmically.

\section{Space Complexity}

In terms of space complexity, the recommendation algorithms utilized in our project have a space complexity of $O(1)$. The space requirements remain constant irrespective of the input size, as the algorithms mainly utilize additional space for storing variables and data structures. This efficient space utilization ensures that the memory consumption does not grow with the size of the available items, making the algorithms efficient in terms of space usage.

\section{Evaluation of Recommendation System}

The recommendation system used in this project demonstrates efficiency, adaptability, accuracy, scalability, and optimal resource usage. By intelligently recommending courses and job skillsets based on factors such as user preferences and similarity measures, the system ensures an optimized learning and career development experience for users. Its adaptability allows for customization to specific user contexts, while its accuracy matches recommendations to users' interests and career goals. With a time complexity of $O(n \log n)$ and a space complexity of $O(1)$, the recommendation system handles a large number of items efficiently and utilizes memory resources optimally. Overall, the recommendation system offers a robust solution for personalized course and job skillset recommendations, enhancing the learning and career development journey for users.
